### 2016-10-24 R/ITHIM.Rmd
Now correct for zero trip times when computing means from NHTS data

The PERSON table contains the family members of the person surveyed,
right?  We want only the peole who were surveyed for their travel
times.  So, we can\'t use everyone in the PERSON table.  If someone
had zero trip time they would not exist in the TRIP table.  So, if we
use just the TRIP table we miss people with zero trip time. So how do
we merge?  We use an inner join and assume that their is a negligible
number of people with zero trip time.  Not very many people never stay
in the house all day.  Please correct me if I am mistaken abiout the
nature of the PERSON or TRIP tables.

```{r subset, eval = compute, fig.width = 10, echo = FALSE}
NHTS.person <- subset( NHTS.person, MSA == TRUE )
NHTS <- merge(NHTS.person, NHTS.trips, by = c("HOUSEID","PERSONID"))
saveRDS(NHTS, file = "./data/NHTS.rds")
```

>>>>

We now correct for zero trip times in NHTS.

```{r subset, eval = compute, fig.width = 10, echo = FALSE}
NHTS.person <- subset( NHTS.person, MSA == TRUE )
NHTS.trips <- subset(NHTS.trips, !is.na(TRPMILES))

NHTS <- merge(NHTS.person, NHTS.trips, by = c("HOUSEID","PERSONID"), all.x = TRUE)
NHTS <- within(NHTS, TRPMILES <- ifelse(is.na(TRPMILES), 0, TRPMILES))
saveRDS(NHTS, file = "./data/NHTS.rds")
```
